---
title: "p8105_hw5_jer2243"
author: "Juliet Rowe"
date: "2023-11-06"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(purrr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```



## Problem 2

```{r}
library(rvest)
```


Importing and tidying the data
```{r}
names = list.files(path="data", full.names=TRUE)

readin_csv = function(path) {
  
  df = 
    read_csv(path) |>
    janitor::clean_names() |>
    mutate(
      ident = path
    ) |>
    separate(ident, into=c("e", "arm", "e2", "id", "csv"), sep=c(5, 8, 9, 11)) |>
  arrange(arm, id) |>
  pivot_longer(week_1:week_8,
               names_to = "week",
               values_to = "value") |>
  separate(week, into = c("w", "week_no"), sep="_") |>
  select(-e, -e2, -csv, -w)
}

output = map(names, readin_csv) |>
  bind_rows()
```

Spaghetti plot of observations on each subject over time
```{r}
output |> 
  mutate(week_no=as.numeric(week_no)) |>
  ggplot(aes(x = week_no, y = value, color = id)) + geom_line() + facet_wrap(~arm)

```
Overall, the values in the experimental arm increased over the weeks while the values in the control arm stayed around the same or slightly decreased. It looks like the experimental arm saw the biggest jumps from weeks 1-3, while the control group jumped up and down with not much of a pattern over the weeks.

## Problem 3

Generate datasets and save mu hat estimates and p-values
```{r}
sim_mean_ttest = function(mu) {
  data = tibble(
    x = rnorm(n=30, mean = mu, sd = 5),
  )

output = data |>
  t.test() |>
  broom::tidy() |>
  select(estimate, p.value) |>
  rename(mu_hat=estimate, pval=p.value)

}

```

Repeat the above for mu = 1, 2, 3, 4, 5, 6
```{r}
sim_results = expand_grid(
  mu_df = c(0, 1, 2, 3, 4, 5, 6),
  iter = 1:5000
) |>
  mutate(
    estimate = map(mu_df, sim_mean_ttest)
  ) |>
  unnest(estimate)
```

Plot showing proportion of times the null was rejected on y axis and the true value of mu on x axis
```{r}
sim_results |>
  group_by(mu_df) |>
  summarize(
    reject = sum(pval<0.05),
    prop = reject/5000
  ) |>
  ggplot(aes(x=mu_df, y=prop)) + geom_line()
```
This plot shows an increasing trend, suggesting that as effect size increases, power also increases (power = the proportion of times the null was rejected).

Plot showing average estimate of mu_hat on y axis and true value of mu on x axis. Overlay a plot of avg estimate of mu_hat only in samples for which the null was rejected on the y axis and true value of mu on x axis.
```{r}

```

